%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background}

\begin{frame}{Noncommutative Geometry} % % % % % % % % % % % % % % % % % % %
    
    \textbf{Unital Spectral Triple} $(\acal , \hcal, D)$: $\hcal$ is a complex separable Hilbert space; $\acal$ is a complex associative intolutive unital $C^*$-algebra with a faithful unital $*$-representation $\acal \hookrightarrow \mathcal B(\hcal)$; a self-adjoint (unbounded) operator $D: \hcal \to \hcal$ with compact resolvent, such that $[D, a] \in \mathcal B(\hcal)$ $\forall a \in \acal$.
    
    \textbf{Canonical Spectral Triple}: Leg $(M, g)$ be an $n$-dimensional compact oriented Riemannian manifold which admits a spin structure% $(Spin_n \to Spin\,M \to M, \eta: Spin\,M \to SO\,M)$
    , and let $\Sigma M$% = Spin\, M \times_\rho \Sigma_n$
    be the associated spinor bundle. Then $(\acal = C^\infty(M), \hcal = L^2(M, \Sigma M), \slashed D = -i \gamma^\mu \nabla^\Sigma_\mu)$%, where $\Sigma_n$ is the $2^{\lfloor n/2 \rfloor}$-dim. fermionic Fock space.
    
    - \textbf{State of $C^*$-algebra} $\acal$ is an $\omega : \acal \to \CC$ linear, positive, of unit norm. \textbf{Pure}: can not be written as a convex combination of other states. Commutative: pure states $\Longleftrightarrow$ characters $\Longleftrightarrow$ points.
    
    - \textbf{Distance}: $d_D(\omega, \omega') = sup_{a \in \acal} \left\{|\omega(a) - \omega'(a)| \, | \, ||[D, a]||_{op} \leq 1 \right\}$
    
    %Compact Quantum Metric Space
\end{frame}


\begin{frame}{The Fuzzy Sphere} % % % % % % % % % % % % % % % % % % %
    \textbf{Fuzzy Space}: %($C^*$? or simply $*$?) 
    family of noncommutative deformations $\acal_n$ of a commutative algebra $\acal$ parametrized by $n \in \bb N$ with increasing dimension and such that $\acal_n \to \acal$ in a suitable sense.
        % \begin{itemize}
        % \item Why? To preserve the (continuous) symmetries of the space while keeping the algebra finite dimensional.
        % \end{itemize}
    
    \textbf{Fuzzy Sphere} with this Dirac Spectral Triples  \cite{DAndrea2013} approximates $S^2$ as: \textbf{1.} $C^*$-algebra acting on the spinor fields $\hcal \cong L^2(S^2)\otimes \CC^2$; \textbf{2.} Representation of $SU(2)$; \textbf{3.}  Metric space on which $SU(2)$ acts by isometries.
    
    - For $N = 2j \in \bb N$, as $SU(2)$ representation $\lbtext{\acal_N}= \bigoplus_{l = 0}^N V_l \hookrightarrow$ $ \bigoplus_{l \in \bb N} V_l \cong L^2(S^2)$, where $V_l$ is the $2l+1$-dimensional irrep. of $SO(3)$ of homogeneous $l$-degree polynomials in $x^1, x^2, x^3$, with basis $\{Y^l_m\}_{|m| \leq l}$. As algebra: $\lbtext{\acal_N} = End(V_j)$ understanding $V_j= \CC^{N+1} =$ $ span\{|j, m\ket\}_{|m| \leq j}$ as irrep. of $SU(2)$; this follows from replacing $x^i \mapsto \frac{1}{\sqrt{j(j+1)}} \pi_{j}(J_i)$ \then $[x^i, x^j] = \frac{1}{\sqrt{j(j+1)}} i \epsilon_{ijk} x_k$.%. Under the adjoint action, it has the irrep. decomposition $\acal_N \cong x$, making it a truncation of $L^2(S)\otimes \CC^2 \cong $
    
\end{frame}