The $2$-sphere $S^2$ as a metric space is $SU(2)$-invariant. This invariance will be seen to give rise to a series decomposition of the canonical Dirac operator on $S^2$. We will see how truncating this $SU(2)$-decomposition of the Dirac operator will give rise to equivariant spectral triples on the fuzzy sphere which inherit some of the nice properties of the canonical spectral triple and which allow the convergence of the fuzzy sphere to $S^2$ also as a metric space, in a precise sense to make precise in section \ref{FSsec:convergence}.

\dbtext{Physical applications of the Fuzzy sphere.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Canonical Spectral Triple of $S^2$}

-- Arising from $SU(2)$ equivariant algebraic Dirac element, in the context of $G$ equivariant spectral triples.

\linea 

Presentation:

(Inherits from $\RR^3$ the metric and the metric connection, but the spinor space changes)

\rtext{Starting point: $SU(2)$-isometries}%\cite{DAndrea2013}
- $S^2$ as the symmetric space $S^3/S^1$ of the compact semisimple Lie group $G = S^3$, $\mathfrak g = su(2)$.
    
- The canonical spectral triple, which is \textbf{$SU(2)$-equivariant} can be seen to come from a purely algebraic element $\lbtext{\mathcal D} \in U(\mathfrak g) \otimes U(\mathfrak g)$:
    \begin{align*}
        U(\mathfrak g) \otimes U(\mathfrak g) &\to& U(\mathfrak g) \otimes Cl(\mathfrak g, -K) &\to& \mathcal B(L^2(G/U, \Sigma G/U)) \\
        1 \otimes 1 + 2 \sum_{k = 1}^3 J_k \otimes J_k &\mapsto& 1 \otimes 1 + \sum_k J_k \otimes \sigma_k &\mapsto& \rtext{\left( \bigoplus_{l\in \bb N} \pi_l \right) \otimes \pi_{1/2}(\mathcal D)}
    \end{align*}
    
(- In Sanchez: $\mu = 1, 2$
 $\nabla_\mu = \partial_\mu - \frac{c_\mu}{q} \sigma_\mu \sigma_{\cut \mu} \cdot$, 
 $\slashed D = -i \frac{q}{2} \sigma^\mu \nabla_\mu)$)

- So $\lbtext{\slashed D} = \begin{pmatrix} 1 + \partial_H & \partial_F \\ \partial_E & 1 - \partial_H\end{pmatrix} = 1 + \partial_F \otimes \sigma_+ + \partial_E \otimes \sigma_- + \partial_H \otimes \sigma_3$ where $\partial_H = -i \partial_\phi$, $\partial_F = e^{i\phi} \left( \partial_\theta + i cot\,\theta \partial_\phi \right)$, $\partial_E = -\partial_F% = e^{-i\phi} \left( \partial_\theta - i cot\,\theta \partial_\phi \right)
$ are the actions of $J_3$, $J^\pm \in i\,su(2)$ on $L^2(S^2)$ respectively. \textit{Eig. vectors}: orth. basis of $\hcal$; \textit{Spectrum} $= \{\pm l\} = \ZZ - 0$ with multiplicities $2l$. (The tensor with $2x\times 2$ matrices means that we are looking at spinors as column vectors $\psi = \begin{pmatrix} \cdot \\ \cdot \end{pmatrix}$)%: L^2(S^2) \otimes \CC^2 \to L^2(S^2) \otimes \CC^2 = \oplus_{l \in \bb N} (\pi_l \otimes \pi_{1/2})(\mathcal D)$

( - The eigenvectors (spinor harmonics) $Y^{'}_{lm}, Y^{''}_{lm}$, $l \in \NN + 1/2$, of $D$ make up an orthogonal basis of the spinor fields $\hcal$.
 - The eigenvalues are: of $Y'_{l\cdot}: (l + 1/2) \in \NN$, of $Y{''}_{l\cdot}: -(l + 1/2)$, with multiplicities $2l+1$)

\linea

Although there are several ways to describe the canonical spectral triple on \todo{of/on?} $S^2$, the one that will be useful to use to define the spectral triples on the fuzzy sphere will be from understanding $S^2$ as \ptext{compact Riemannian symmetric\footnote{Symmetric space; U} space} $S^2 \cong G/U$ of the compact semisimple Lie group $G = SU(2)$.

Let $G$ be a compact semisimple Lie group $G$ with Lie algebra $\alg g$, where the semisiplicity means that the Killing form $K: \alg g \times \alg g \to \alg g$ of $\alg g$ is negative definite, giving $G$ a natural Riemannian manifold structure. For such a manifold $G$, and its symmetric spaces, the Dirac operator can be seen to arise \ref{} from an algebraic element $\lbtext{\dcal } \in U(\alg g)\times U(\alg g)$, where $\lbtext{U}(g)$ is \lbtext{the universal enveloping algebra} of the Lie algebra $\alg g$, i.e. the largest\todo{in what sense} \todo{complex?} unital, associative algebra containing $\alg g$ where the Lie bracket coincides with the commutator in $U(\alg g)$; it is important to remark that \otext{the representations of $\alg g$ are in a bijective correspondence with the modules over $U(\alg g)$}. In the explicit case where $G = SU(2)$,
\begin{equation}
    \lbtext{\dcal} := 1 \otimes 1 + 2 \sum_{k = 1}^3 J_k \otimes J_k \in U(\sut) \otimes U(\sut)
\end{equation}
where $J_k \in U(\sut), k = 1, \dots, 3$ are the basis of $\sut\otimes \CC$ such that $[J_i, J_j] = i \epsilon_{ijk} J_k$ (i.e. $J_k = \frac{\sigma_k}{2} = \pi_{1/2}(J_k)$). 

\lin

Let $\lbtext{\pi_j}: U(\sut) \to M_{2j+1} = End(\CC^{2j+1})$ be the spin $j \in \frac{\NN}{2}$ representation of $\sut$ where each element of the canonical basis $e_m \in \CC^{2j+1}$, $m = -j, \dots, j-1, j$ satisfies $\pi_j(\vec J^2)(e_m) = j(j+1) e_m$ and $\pi_j(J_3)(e_m) = m e_m$, where $\vec J^2$ is notation for $J_1^2 + J_2^2 + J_3^3 \in U(\sut)$.

Recall that the every continuous / square integrable / smooth function on $S^2$ may be decomposed in terms of spherical harmonics $Y^l_m \in L^2(S^2)$, $l \in \NN$, $m \in \{-l, \dots, l-1, l\}$, and the spaces $\tilde V_l = span\{Y^l_m\}_{|m| \leq l}$ for fixed $l$ are the spaces of homogeneous polynomials on the coordinates $x^1, x^2, x^3$ of $\RR^3$, which are precisely all the irreducible representation spaces of $SO(3)$, and another description of the spin-$l$ representations $V_l$ of $SU(2)$. 
This decomposition of $L^2(S^2)$ is in fact the one induced by the action of $SU(2)$, inherited from the action on $S^2$, and which can be seen to be induced by the natural action of $\sut$ on $S^2$ as vector fields. In particular, 
\begin{align}
    \partial_H &:= - i \partial_\phi & \text{is the action of $\lbtext{H} := J_3$ in $L^2(S^2)$} \\
    \partial_F &:= e^{i\phi} \left( \partial_\theta + i cot\,\theta \partial_\phi \right) &\text{is the action of $\lbtext{F} := J_+ = J_1 + i J_2$ in $L^2(S^2)$}\\
    \partial_E &:= - \partial_E &\text{is the action of $\lbtext{E} := J_- = J_1 - i J_2$ in $L^2(S^2)$}
\end{align} where $\phi$ and $\theta$ are the azimuthal and polar angles in $S^2$, respectively.
Hence, $L^2(S^2) \cong \bigoplus_{l = 0}^\infty V_l$ as representation spaces of $SU(2)$.

The spinor bundle of $S^2$ is trivial, so the space of spinor fields $\hcal = L^2(S^2, \Sigma S^2)$ of $S^2$ is isomorphic (as a vector space) to $L^2(S^2) \otimes \CC^2$, where $\CC^2$ is understood as the \textit{fermionic Fock space} associated to the tangent spaces of $S^2$, i.e. the unique irreducible representation of the Clifford algebra $\CC l_2 = M_2(\CC) = \pi_{1/2}(U(\sut))$. Therefore, \rtext{the spinor bundle of $S^2$ decomposes as representation of $SU(2)$ as $L^2(S^2, \Sigma S^2) \cong \bigoplus_{l = 1}^\infty V_l \otimes V_{1/2}$}.

\lin

This decomposition of the spinor bundle induced by the action of $SU(2)$ correctly suggests that the Dirac operator can be seen as the operator
\begin{equation}
    \lbtext{\slashed D} = \rtext{ \bigoplus_{l\in \bb N} \pi_l  \otimes \pi_{1/2}(\dcal)} = 1 + \partial_F \otimes \sigma_+ + \partial_E \otimes \sigma_- + \partial_H \otimes \sigma_3 = \begin{pmatrix} 1 + \partial_H & \partial_F \\ \partial_E & 1 - \partial_H\end{pmatrix} ,
\end{equation} acting on $L^2(S^2)\otimes \CC^2$, where $\sigma \pm = \sigma_1 \pm i \sigma_2$.

The eigenvectors of $\slashed D$ $Y^{'}_{jm}, Y^{''}_{jm}$ $j \in \NN + 1/2$, $m = -j, \dots, j$, called the \textit{spinor harmonics}, make up an orthogonal basis of the spinor fields $\hcal$. The eigenvalue of the $Y'_{l\cdot}$ is $(j + 1/2) \in \NN$, and of the $Y{''}_{j\cdot}: -(l + 1/2)$, so the eigenvalue $j$ has multiplicity $2j+1$. The spectrum of $\slashed D$ (and the respective multiplicities) will be an indication of how good of an approximation is another Dirac operator in the Fuzzy sphere. 


\linea

(The following was previously right after the paragraph about the representations of $SU(2)$, but may now be unnecesary)

Now, to $\dcal \in U(\alg g) \otimes U(\alg g)$ corresponds an element $\dcal_S$ in the noncommutative Weil algebra\footnote{CCR algebra of $(\alg g, \omega?)$. } through the injection $\alg g \hookrightarrow Cl(g, K)$/$\alg g_\CC \hookrightarrow \CC l(G/U)?$\todo{not sure we want here the real algebra, and I even think we want instead the complex algebra since it is that one which acts on Fock space}\todo{not even sure if we want this CLifford algebra, of the one before, since it is that one which acts on the spinors on $S^2$, and so it is true that $\CC l_2 = M_2(\CC)$}\footnote{Clifford algebra}. It is known that, for a $3$ dimensional real vector space $V$ with positive definite metric with basis $\{v_k\}_{k = 1, \dots, 3}$, the real Clifford algebra $Cl(V, g) \cong gen\{\sigma_k\}_{k = 1, \dots, 3} = gen\{J_k\}_{k = 1, \dots, 3} = M_2(\CC)$ and $\CC l(V) \cong M_2(\CC) \oplus M_2(\CC)$ under the identification $v_k \Longleftrightarrow \sigma_k \in M_2(\CC)$, meaning, for our explicit example, that the algebra $Cl(\sut, -K) = M_2(\CC)$ 
\todo{there is an $i$ which I don't like when saying this last sentence}, and so the injection can be seen to be simply $\pi_{1/2} = Id_2$:
\begin{equation}
    \dcal_S := (Id_2 \otimes \pi_{1/2})(\dcal) = 1 \otimes 1 + \sum_{k = 1}^3 J_k \otimes \sigma_k = \begin{pmatrix} 1 + H & F \\ E & 1 - H \end{pmatrix} \in U(\sut)\otimes M_2(\CC)
\end{equation}
where $H = J_3$, $E = J_1 + iJ_2$ and $F = E^* \in U(\sut)$


Equivariance of $\dcal$: $U(\alg g)$ is a Hopf algebra\footnote{} with coproduct $\nabla: U(\alg g) \to U(\alg g) \times U(\alg g)$ such that $A \mapsto A \otimes 1 + 1 \otimes A$ for $A \in \alg g$.

\lin 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Fuzzy Sphere}

 -- Change $x_i$ in $\RR^3$ by infinitesimal rotation $J_i$, acting on $\CC^{N+1} = span\{|j, m\rangle\}$.

Presentation:

\textbf{Fuzzy Space}: ($C^*$? or simply $*$?\todo{}) 
    family of noncommutative finite dimensional $\acal_n$ parametrized by $n \in \bb N$ with increasing dimension and such that that approximate the commutative algebra $\acal$. Why? \textit{Keep continuous symmetries}.
        % \begin{itemize}
        % \item Why? To preserve the (continuous) symmetries of the space while keeping the algebra finite dimensional.
        % \end{itemize}
    
    \textbf{Fuzzy Sphere}: Notice that $\acal \cong \bigoplus_{l \in \bb N} V_l \cong L^2(S^2)$, where $V_l$ is the spin $l$ representation of $SO(3)$: homogeneous $l$-degree polynomials in $x^1, x^2, x^3$, with basis $\{Y^l_m\}_{|m| \leq l}$. 
    For $N = 2j \in \bb N$, 
    $\lbtext{\acal_N}= \bigoplus_{l = 0}^N V_l$ as $SU(2)$ representation. 
    As algebra: replacing $x^i \mapsto \frac{1}{\sqrt{j(j+1)}} \pi_{j}(J_i)$, $[J_i, J_k] = i \epsilon_{ijk} J_k$, $\lbtext{\acal_N} := End(V_j) = M_{N+1}(\CC)$, understanding $V_j= \CC^{N+1} = span\{|j, m\ket\}_{|m| \leq j}$ as irrep. of $SU(2)$; this follows from  $\longrightarrow$ \rtext{$[x^i, x^j] = \frac{1}{\sqrt{j(j+1)}} i \epsilon_{ijk} x_k$}, $\sum x_1^2 + x_2^2 + x_3^2 = 1$.
    
    With these Dirac Spectral Triples \cite{DAndrea2013} \rtext{approximates $S^2$ as: \textbf{1.} $C^*$-algebra $\acal$ acting on the spinor fields $\hcal$; \textbf{2.} Representation of $SU(2)$; \textbf{3.}  Metric space on which $SU(2)$ acts by isometries.}
    
    %. Under the adjoint action, which makes sense since R J_3 R^{-1} is rotation under rotated axis
    
    % This allows to define fuzzy spherical harmonics (changing x's by new x's) which make up a basis, good action under SU(2)
    
\linea

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Spectral Triples}

 --  Truncate the $SU(2)$-equivariant \textbf{decomposition} of the canonical spectral triple

(The tensor with $2x\times 2$ matrices means that we are looking at spinors as column vectors $\psi = \begin{pmatrix} \cdot \\ \cdot \end{pmatrix}$)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Irreducible Spectral Triple}
 
 - One term of the canonical spectral triple
 
Presentation:

A first spectral triple is simply taking ``one term'' of $\slashed D$:
\begin{multline}
    \lbtext{D_N} 
    := (\pi_j \otimes \pi_{1/2})(\mathcal D): V_j \otimes \CC^2 \to V_j \otimes \CC^2 \\
    = \begin{pmatrix} 1 + \pi_j(H) & \pi_j(F) \\ \pi_j(E) & 1 - \pi_j(H)\end{pmatrix} 
    = 1 + \pi_j(F) \otimes \sigma_+ + \pi_j(E) \otimes \sigma_- + \pi_j(H) \otimes \sigma_3
\end{multline} where $H = J_3$, $F = J_+$, $E = J_-$ are the actions of $J_3$, $J^\pm \in su(2)$ on $V_j$ respectively.

- The spectral triple \rtext{$(\acal_N, \lbtext{H_N} = V_j \otimes \CC^2, D_N)$}
    \begin{itemize}
        
    \item Is $SU(2)$-equivariant
    
    \item Has eigenvalues $j+1$ and $-j$ with multiplicities $2j+2$ and $2j$.
        
    \item Isn't compatible with a grading or a real structure.
    \end{itemize}
    
\linea




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Full Spectral Triple}

- Truncation of the canonical spectral triple. In particular the Dirac operator ``goes'' to the canonical one.

Presentation:

\rtext{$(\acal_N, \lbtext{\hcal_N} := \mathcal A_N \otimes \CC^2 \cong \bigoplus_{l =1}^N H_l, \mathcal D_N \longleftrightarrow \bigoplus_{l =1}^N D_l)$}, where:
\begin{multline}
    \lbtext{\mathcal D_N} := (\textbf{ad}\pi_j \otimes \pi_{1/2})(\mathcal D) = D = \begin{pmatrix} 1 + \text{ad}\pi_j(H) & \text{ad}\pi_j(F) \\ \text{ad}\pi_j(E) & 1 - \text{ad}\pi_j(H)\end{pmatrix} 
    = \text{ad}\pi_j(E) \otimes \sigma_1 + \text{ad}\pi_j(F) \otimes \sigma_2 + \text{ad}\pi_j(H) \otimes \sigma_3
\end{multline}
where, e.g. $\text{ad}\pi_j(H) = [\pi_J(H), \cdot ]$ is the action of $J_3 \in su(2)$ on $\mathcal A_N$.

    \begin{itemize}
    
    \item It is a real spectral triple.
    
    \item It is $SU(2)$-equivariant
    
    \item Spectrum of $\mathcal D_N$ is the truncation of $\slashed D$ to $\{-N, \dots, N+1\}$. The eigenvalues of $\mathcal D_N$ are $N+1$ with multiplicity $2N+2$, and $\pm l$ with multiplicity $2l$ for $l = 1, \dots, N$
    
    \item It is not compatible with a grading.
    
    \end{itemize}

\rtext{It is a truncation of the canonical spectral triple}: The spectrum and the multiplicites 

- \rtext{\textbf{Theorem}}: the two spectral triples induce the same distance in $\acal_N$. Pf: $[\dcal, a]b \otimes v = \cdots = \sum_k [\pi_j(J_k), a]b \otimes \sigma_k v = [D_N, a] \cdot b \otimes v$

\linea

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coherent States}

-- Fuzzy approximations of points in S2. In QM they are the closes thing to classical states we have (minimum uncertainty states for some observables).

- \dbtext{Are they pure}? They are vector states, I think that suffices to make them pure.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SHO Coherent States}

3 characterizations. Heisenberg group.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$SU(2)$-Coherent States}

 - Rotations of $|j, -j \rangle$
 
Presentation:

- The Bloch/$SU(2)$-\rtext{coherent states} are for the group $SU(2)$ what the usual harmonic oscillator coherent states are for the Heisenberg group. In particular, they are minimum uncertainty states. 

- \rtext{They will be considered fuzzy approximations of the points of $S^2$}.

- \rtext{Points of the $E(\phi, \theta) \in S^2$ sphere are approximated by coherent vectors} $\lbtext{|\phi, \theta)_N} := R_{(\phi, \theta)}|j, -j\rangle \in V_j \Longleftrightarrow $ states of $\mathcal A_N = End(V_j)$ $\lbtext{\psi^N_{(\phi, \theta)}} = (\phi, \theta| \cdot |\phi, \theta)_N \in \mathcal S(\mathcal A_N)$. 

- \rtext{This identification of points in $S^2$ with coherent states ($\psi^N: \acal_N \to L^2(S^2)$ at the algebra level\todo{})
is $SU(2)$-equivariant}: $g_* \psi^N_{(\phi, \theta)} = \psi^N_{g\cdot (\phi, \theta)}$, \& \rtext{the distance between them is $SU(2)$-invariant}.

What group used in Fiore? $O(D)$

- In Fiore2020 there is a simple introduction to Coherent states: group $G$ acting (irreducibly) on a Hilbert space. AND the example for $G = SU(2)$ is sketched, although there is a mistake for one of the $3$ characterizations, since it isn't true that the coherent states are eigenvectors of the ``annihilation operator'' $J_+$. D'Andrea mentions other sources.

\linea
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Distance Between Famillies of \dbtext{Pure} States}

Presentation:

\textit{From now on}: we use the irreducible s.t. and not write the $\pi_j$'s.

- The supremum $d_D(\omega, \omega')$ is always attained in hermitian elements.

- For $a \in \acal_N$, 
\begin{equation} \label{ineqDN}
    ||[H, a]||, ||[E, a]||, ||[F, a]||  \leq ||[D_N, a]||;
\end{equation} \label{eqDNdiag}
if $a$ is diagonal hermitian, then
\begin{equation}
    ||[E, a]|| = ||[D_N, a]||.
\end{equation}

- A state may be defined only on hermitian elements of $\acal$, since from there it can be uniquely extended to all $\acal$: $a = \frac{a+a^*}{2} + \frac{a - a^*}{2} \in Herm. + Antiherm. = Herm. + i\, Herm.$

\linea

- \textbf{Procedure}: Understand $||[D, a]||$; find upper limit for $|\omega(a) - \omega(a')|$ dependent on $||[D, a]||$; find hermitian algebra element that saturates the inequality (or sequence that get close) (if inequalities depending on $||[D, a]||$ are found, this element will need to have a maximizing $||[D, a]||$, probably $1$). 

Very similar procedure to calculate distances followed in Chakraborty Moyal Plane and Chakraborty Fuzzy Sphere.

- \textbf{Discrete Basis States}: In $\acal_N = End(V)$, study vector states of important basis, relating $\omega_m(a) - \omega_n(a)$ to $[D_N, a]$.

- \textbf{$G$-invariance of distance}: if $G$ acts by ``isometries'', simplify what needs to be proven.

- \textbf{Auxiliary distance}: study simpler subalgebra distance: lower bound whose behavior is understood and that encases the actual distance, allowing approximate study.

- \textbf{Behaviour with $N$}: Relate algebras and coherent states of subsequent $N$, finding relation between $||[D_{N+1}, \cdot]||$ and $||[D_N, \cdot]||$.

\linea

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$SU(2)$-invariance of the distance}

 - If $G$ acts by ``isometries'', simplify what needs to be proven.

Presentation:

$SU(2) \ni g$ acts on the states: $\lbtext{g_*\omega}(\cdot) := \omega(\cdot^g)$ $\longleftarrow$ it acts on the algebra: $\lbtext{a^g}:= g\circ a \circ g^* \cdot$ $\longleftarrow$ it acts on $V_j$: $\pi_j(g)$.

\textbf{\rtext{Theorem}}: For all $N = 2j \in \bb N$, the distance is $SU(2)$-invariant: 
\begin{align}
    d_N(\omega, \omega') &= d_N(g_* \omega, g_*\omega'), & \text{for all $\omega, \omega' \in \mathcal S(\acal_N)$}.
\end{align}

\textit{Pf}: The theorem follows once we show 
    \rtext{$||[D_N, a^g]|| = ||[D_N, a]||$}:
$d_N(g_* \omega, g_* \omega') = sup_{a \in \acal_N}\{ |\omega(a^g) - \omega'(a^g)|: ||[D_N, a \otimes 1_2]|| \leq 1 \} = sup_{b \in \acal_N}\{ |\omega(b) - \omega'(b)|: ||[D_N, b \otimes 1_2]|| \leq 1 \} = d_N(\omega, \omega')$, where $b = a^g$ sweeps all $\acal_N$.

\textit{Pf}: $[D_N, a^g \otimes 1] = u[D_N, a \otimes 1_2]u^*$ where $u = \pi_j(g) \otimes \pi_{1/2}(g)$ is the induced unitary action of $g$ in $H_N$ $\xleftarrow{}$
1. $a^g \otimes 1_2 = u(a \otimes 1_2)u^*$;
2. The spectral triple is $SU(2)$-equivariant, hence $D_N$ commutes with the $SU(2)$ action.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The $N=1$ distance between coherent states}

 - 
 
 Presentation:
 
$\pi_{1/2}(J_k) = \sigma_k/2$

- Any hermitian element in $\acal_1 = M_2(\CC)$ can be written as
\begin{align*}
    a &= \begin{pmatrix} a_0 + a_3 & a_1 - i a_2 \\ a_1 + i a_2 & a_0 - a_3  \end{pmatrix}= a_0 + \vec a \cdot \vec \sigma, & \text{for $(a_0, \dots, a_3) \in \RR^4$.}
\end{align*}


- Positivity of states implies that, restricted to hermitian elements, they all are  $\omega_{\vec x}(a) = a_0 + \vec x \cdot \vec a$, for $\vec x \in B^3 \subset \RR^3$.

- $\omega_{\vec x}$ is pure $\iff$ $\vec x = (\sin \theta \cos \phi, \sin \theta, \cos \theta) \in S^2$ $\dbtext{\iff}$ $\omega_x = \psi^1_{(\phi, \theta)}$.

\rtext{\textbf{Theorem}}: For $N = 1$ all pure states are coherent states and 
\begin{equation}
    d_1(\hat p, \hat q) = \frac{1}{2}|\vec p - \vec q|_{\RR^3}
\end{equation}
\textit{Pf}: $|\omega_{\vec x}(b) - \omega_{\vec y}(b)| = |(\vec x - \vec y)\cdot \vec b| \leq |\vec x - \vec y||\vec b|$; $i[D_1, a]$ is hermitian with max. eigenvalue/norm $=2 |\vec a|$ $\longrightarrow$ $a \in \acal_1$ hermitian with $\vec a$ parallel to $\vec x - \vec y$ st. $2|\vec a| = 1$ saturates the inequality.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Distance Between (Vector) Discrete States $|j,n\rangle$ for Arbitrary $N$}

Presentation:

\rtext{\textbf{Theorem}}: For any $N$, let $\lbtext{\omega_m} = \langle j, m| \cdot |j, m\rangle \in \mathcal S(\acal_N)$ (SP $\Longleftrightarrow |j, -j\rangle$, NP $\Longleftrightarrow |j, j\rangle$):
\begin{equation}
    d_N(\omega_m, \omega_n) = \sum_{k = m+1}^n \frac{1}{\sqrt{(j+k)(j-k+1)}} = \sum_{k = m+1}^n d_N(\omega_{k-1}, \omega_k)
\end{equation}
%  and so, between the north and south poles
% \begin{equation}
%     d_N(\psi_{(0,0), \psi_{(0, \pi)}}) = \sum_{k = 1}^N \frac{1}{\sqrt{k(N-k+1)}}
% \end{equation}
\textit{Pf}: Recall that $J_\pm|j,m\rangle = \sqrt{(j\mp m)(j\pm m + 1)}|j, m+1 \rangle$ $\longrightarrow$ $\omega_m(a) - \omega_n(a) = \sum_{k = m+1}^n \langle j, k-1 |a|j, k-1 \rangle - \langle j, k |a| j, k \rangle = \sum_{k = m+1}^n \frac{1}{\sqrt{(j+k)(j-k+1)}} \langle j, k| [E, a] |j, k-1 \rangle$; since $|\langle j, k |[E, a]|j, k-1 \rangle|  \leq ||[E, a]|| \leq ||[D_N, a]|| \leq 1$, we get the upper bound. 

Define the diagonal hermitian operator $\hat a |j, m\rangle := - \left( \sum_{k = -j+1}^m  \right)|j, m\rangle$, $\longrightarrow$ $[E, \hat a] |j, k \rangle = |j, k+1\rangle$ ($k < j$), and so $\hat a$ saturates the inequality.

\linea
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Relating Distinct $N$'s and Upper Bound}

 - Relate algebras and coherent states of subsequent $N$, finding relation between $||[D_{N+1}, \cdot]||$ and $||[D_N, \cdot]||$.
 
Presentation:

\rtext{\textbf{Theorem}}: the distance $d_N(\psi^N_{(\phi, \theta)}, \psi^N_{(\phi', \theta')})$ is non-decreasing with $N$:
\begin{equation}
    d_N(\psi^N_{(\phi, \theta)}, \psi^N_{(\phi', \theta')}) \leq d_{N+1}(\psi^{N+1}_{(\phi, \theta)}, \psi^{N+1}_{(\phi', \theta')})
\end{equation}

 KEY: Relate $N$ with $N+1$
 
\textit{Pf}: $U^\pm_j |\phi, \theta)_{N+1} = |\phi, \theta)_N \otimes |\phi, \theta)_1$, $\xrightarrow{}$ $\eta^+_N: \acal_N \to \acal_{N + 1}$ $\longrightarrow{}$ $\psi^{N+1}_{(\phi, \theta)} \circ \eta^+_N(a) = \psi^N_{(\phi, \theta)}$ \& $||[D_{N + 1}, \eta^+_N(a)]|| \leq ||[D_N, a]||$.

\rtext{\textbf{Theorem}}: For all $N$, 
\begin{equation}
    \frac{1}{2}|E(\phi, \theta)- E(\phi', \theta')| \leq || \leq d_N(\psi^N_{(\phi, \theta)}, \psi^N_{(\phi', \theta')}) \leq d_{geo}(E(\phi, \theta), E(\phi', \theta')).
\end{equation}

\textit{Pf}: \textbf{use SU(2)-invariance of distance} and only prove it between within the great circle $\theta = \frac{\pi}{2}$: $d_N(\psi^N_{(0, \frac{\pi}{2})}, \psi^N_{(\phi, \frac{\pi}{2})}) \leq |\phi|$. 
$|\psi^N_{(\phi, \frac{\pi}{2})} - \psi^N_{(0, \frac{\pi}{2})}| = |i \int_0^\phi \psi^N_{(\alpha, \frac{\pi}{2})}([H, a]) d\alpha | \leq ||[H, a]|| |\phi| \leq |\phi| ||[D_N, a]||$.

(Dibujito: $N=1$ en un color, other increasing $N's$ (equivalent paths), finally commutative distance).

\linea

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Auxiliary Distance and Limit}
 - Study simpler subalgebra distance: lower bound whose behavior is understood and that encases the actual distance, allowing approximate study.

Presentation:

Distance along diagonal, hermitian matrices eassier to understand, but useful.

 KEY: find simpler (we understand [D, a] if a is diagonal hermitian), but useful auxiliary distance (gives a lower bound that sandwhiches the actual distance)
 
Let $\lbtext{\bcal_N} \subset \acal_N$ be sugalgebra of diagonal matrices $\xrightarrow{}$ $\psi^N_{(\phi, \theta)} = \psi^N_{(0, \theta)}$, now 
$\lbtext{\rho_N}(\theta) := sup_{a \in \bcal_N, a = a^*}\{|\psi^N_{(0, \theta)} - \psi^N_{(0, 0)}| : ||[D_N, a]|| \leq 1\}$: \textbf{1.} exact formula related to $\omega_m$ states, \textbf{2.} $0 \leq \rho'_N(\theta) \leq 1$ $\xrightarrow{}$ $\rho_N(\theta) \leq \theta$, \textbf{3.} non-decreasing with $N$.


\textbf{Lemma}: For all $N$, 
\begin{align*}
    1.& \rho_N(\theta - \theta') \leq d_N(\psi^N_{(\phi, \theta)}, \psi^N_{(\phi', \theta')}) d_{geo}(E(\phi, \theta), E(\phi', \theta'))  ; \\
    2.& \text{the sequence $\rho_N(\theta)$ converges uniformly to $\theta$ as $N\to \infty$} \leq .
\end{align*}

\textbf{\rtext{Theorem}}:  
\begin{equation}
        \lim_{N \to \infty} d_N(\psi^N_{(\phi, \theta)}, \psi^N_{(\phi', \theta')}) = d_{geo}(E(\phi, \theta), E(\phi', \theta'))
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Convergence of fuzzy sphere to $S^2$}\label{FSsec:convergence}

 - This identification of points in $S^2$ with coherent states ($\psi^N: \acal_N \to L^2(S^2)$ at the algebra level) \todo{???}
is $SU(2)$-equivariant: $g_* \psi^N_{(\phi, \theta)} = \psi^N_{g\cdot (\phi, \theta)}$, \& \rtext{the distance between them is $SU(2)$-invariant}.
 
 - as: \textbf{1.} $C^*$-algebra $\acal$ acting on the spinor fields $\hcal$; \textbf{2.} Representation of $SU(2)$: homeomorphisms?\todo{homeomorphisms? Symmetries?}; \textbf{3.}  Metric space on which $SU(2)$ acts by isometries.
